Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-04-09 journal-draft/bare_jrnl_comsoc.tex
polished proof of 5.1

When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
Thus, when a instance $\mathcal{I}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
%%Meanwhile, the number of common channels of all the other single node cluster is 0.
the summed number of CCCs of the clusters in the mapped CRN is always smaller than $\lambda$.

>>>>

When there are only disjoint sets in an instance $\mathcal{I}$ for weighted k-set packing, the sum weight is identical to the sum number of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains sets which only have one element.
Thus, when a instance $\mathcal{I}$ for k-set packing problem is true, \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
In the other way around, when an instance if false for weighted k-set packing problem,
%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
%%Meanwhile, the number of common channels of all the other single node cluster is 0.
the summed number of CCCs of the clusters in the mapped CRN is smaller than $\lambda$, and there is no clustering solution satisfying the centralized clustering problem.
